Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-24 paper.tex
feat: biblio
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

% Conclusion
\section{Conclusion}
The personal photometric observations of U Cephei conducted in this study illustrate the potential for amateur astronomers to achieve a high degree of precision, even in light-polluted environments. These observations, while slightly less precise than professional datasets, offer valuable insights and demonstrate the viability of citizen science in advancing binary star research. Further research should focus on refining techniques and fostering collaborative efforts between amateur and professional astronomers to maximize the scientific value of such observations.

% References
\begin{thebibliography}{99}
\bibitem{example1} Smith, J., "Photometric Studies of Binary Stars," \textit{Astrophysical Journal}, vol. 123, no. 4, pp. 567-578, 2020.
\bibitem{example2} Brown, A., \textit{Amateur Contributions to Astronomy}, Cambridge University Press, 2018.
\bibitem{example3} Doe, R., "Comparative Analysis of Amateur and Professional Astronomical Data," \textit{Astronomy and Astrophysics}, vol. 456, no. 3, pp. 234-245, 2019.
\end{thebibliography}

\end{document}

>>>>

% Conclusion
\section{Conclusion}
The personal photometric observations of U Cephei conducted in this study illustrate the potential for amateur astronomers to achieve a high degree of precision, 
even in light-polluted environments. These observations, while slightly less precise than professional datasets, 
offer valuable insights and demonstrate the viability of citizen science in advancing binary star research. 
Further research should focus on determining why we have a magnitude variation difference between the amateur and professional data,
therefore we could get data from less polluted areas to see if the difference is due to the light pollution or to the equipment used.

% References
\begin{thebibliography}{9}

    \bibitem{TESS}
    NASA TESS Mission,
    \textit{The Transiting Exoplanet Survey Satellite (TESS)}, 
    \url{https://www.nasa.gov/tess}, accessed January 2025.

    \bibitem{AAVSO}
    American Association of Variable Star Observers,
    \textit{Variable Star Charts, Data and Resources}, 
    \url{https://www.aavso.org}, accessed January 2025.

    \bibitem{Siril}
    Siril,
    \textit{Free Astronomical Image Processing Software},
    \url{https://siril.org/}, accessed January 2025.

    \bibitem{AstroImageJ}
    Collins, K. A., Kielkopf, J. F., Stassun, K. G., Hessman, F. V. (2017). 
    \textit{AstroImageJ: Image Processing and Photometric Analysis Software for Astronomical Research}.
    The Astronomical Journal, 153(2), 77.

    \bibitem{LightPollution}
    International Dark-Sky Association (IDA), 
    \textit{Understanding Light Pollution}, 
    \url{https://www.darksky.org}, accessed January 2025.

    \bibitem{SatellitePhotometry}
    Guinan, E. F., Engle, S. G., Devinney, E. J. (2014). 
    \textit{A Satellite Constellation for Photometry and Monitoring of Variable Stars}. 
    Journal of the American Association of Variable Star Observers, 42, 235. 
    \url{https://ui.adsabs.harvard.edu/abs/2014JAVSO..42..235G/abstract}, accessed January 2025.

    \bibitem{AmateurObservation}
    Mobberley, M. (2010). 
    \textit{Amateur Astronomer's Handbook}. 
    Springer, Chapter 1. 
    \url{https://link.springer.com/content/pdf/10.1007/978-1-4471-0055-3_1.pdf}, accessed January 2025.

    \bibitem{AmateurContribution}
    Mattei, J. A. (1990). 
    \textit{The Contribution of Amateur Astronomers to the Study of Variable Stars}.
    Proceedings of the International Astronomical Union, 125, 73. 
    \url{https://www.cambridge.org/core/services/aop-cambridge-core/content/view/6E3175E20C284177D4F534F506B1DD3E/S0252921100092794a.pdf/the-contribution-of-amateur-astronomers-to-the-study-of-variable-stars.pdf}, accessed January 2025.

    \bibitem{VariableStar}
Wikipedia,
\textit{Variable Star}, 
\url{https://en.wikipedia.org/wiki/Variable_star}, accessed January 2025.

    \end{thebibliography}
\end{document}
